LHC abort gap monitor electronics upgrade

### 2024-04-25 paper.tex
edited summary

\section{Control Interface}
The gateware outputs data from four different block rams. The first stores raw
data from the ADC, that is used correctly set the initial delay of the
instrument's timing. It stores 1.5 turns and therefore it is published with
\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
averaged data taken every \SI{10}{ms} defining the publishing rate. The
fetching handles the FESA server, which obtains interrupt every time the data
are ready. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{New AGM expert graphical interface}
    \label{fig:control_interface}
\end{figure}
To simplify the setup tunining a new interface had to be created. It runs as
client of FESA server and displays the content of all the block rams. The main
control panel is depicted in Fig. \ref{fig:control_interface}. It displays
three plots, raw data from the ADC (top plot), processed averaged data (down
plot on the left) and and evolution of the data in time (down plot on the
right). The menu on the left controls the amplifier and bottom menu controls
the acquisition delays and optical filters.

@@

\section{Summary}
The AGM has been implemented on the VFC-HD carrier board simplifying
maintenance. The implementation is based on the direct digital conversion,
which eliminates artefacts in the output plot from the current system using
IBMS cards embedding analog integrators. It also solves the calibration hassle. 
The comparison of the two systems is summarized in the following table Tab.
\ref{tab:system_comparison}.
\input{tables/system_comparison.tex} 
The system is installed in the point 4 next to the current AGM collecting data
to be further analyzed. For the complet reliability test and proper function
verification, it needs to be collected more data and they have to be compared
with the current system. The systems shows so far, that with less light, it can
have still similar results to the current AGM.

>>>>

\section{Control Interface}
The gateware outputs data from four different block rams. The first stores raw
data from the ADC, that is used correctly set the initial delay of the
instrument's timing. It stores 1.5 turns and therefore it is published with
\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
averaged data taken every \SI{10}{ms} defining the publishing rate. The
fetching handles the FESA server, which obtains interrupt every time the data
are ready. 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{New AGM expert graphical interface}
    \label{fig:control_interface}
\end{figure}
To simplify the setup tunining a new interface had to be created. It runs as
client of FESA server and displays the content of all the block rams. The main
control panel is depicted in Fig.~\ref{fig:control_interface}. It displays
three plots, raw data from the ADC (top plot), processed averaged data (down
plot on the left) and and evolution of the data in time (down plot on the
right). The menu on the left controls the amplifier and bottom menu controls
the acquisition delays and optical filters.

@@

\section{Summary}
The new AGM has been implemented on the CERN BI standard platform VFC-HD
carrier simplifying maintenance. The design removed the IBMS cads with ASIC
lhcb2002b and so resolved the issue with cumbersome calibration and artefacts
in the output plots.  It also The changes in the AGM design compared to the
current AGM are summarized in the following table Tab.
\ref{tab:system_comparison}.
\input{tables/system_comparison.tex} 
The system is installed in LHC the point 4 next to the current AGM collecting data
to be further analyzed. For the complet reliability test and proper function
verification, it needs to be collected more data, that will help evalate system
goodness. The systems shows so far, that with less light, it can have still
comparable outputs to the current AGM.
